Scheduling and Vectorization for MPC

### 2022-03-16 overleaf/biometric_vectorization_example.tex
put paper latex sources in 'overleaf' folder

In the code below, all initializations (e.g., \texttt{min\_sum!3 = i}), operations, and PHI nodes are \emph{implicitly vectorized}. 
$\mathit{raise\_dim}$ and $\mathit{drop\_dim}$ statements, as well as propagation statements (e.g., \texttt{min\_sum!3 = sum!3\^}) 
may have slightly different interpretation. \ana{This is vague, may need elaboration.}

Note the two different versions of $\mathit{raise\_dim}$. \ana{More here! One just adds a least-significant dimension. The other one may reshape an input array.}

@@

\ana{Begin Work-in-progress notes on implementation. Just some thoughts...} 
\begin{comment}
For now, I suggest we go with a "naive" implementation and try to do only minimal optimizations. 
All arrays are stored in the program as one-dimensional arrays. Arrays lifted from scalars have dimensionality of the loop enclosure in 
the original code, e.g., \texttt{sum!3} is two dimensional \texttt{[N!0,D!0]} (but represented linearly in row-major order; all these "copies" are 
arrays of references to shares). Naturally, all writes into these arrays are canonical writes, i.e., $A[i,j] = ...$ and no things like $A[i+1,j-1] = ...$.

@@

\begin{verbatim}
// project the (j-1)-st column vector:
A = sum!4[I,j-1]
// project j-th column from p!3: 
B = p!3[I,j] 
// we get a N!0-size vector of references to NEW shares:
C = ADD_SIMD(A,B) 
// Writes j-th column of sum!4 with the new references:
sum!4[I,j] = C 
// may eventually optimize since C is A
\end{verbatim}
\end{comment}
There are three kinds of arrays (for now all kept internally as one-dimensional arrays, but that's under discussion).
\begin{itemize}

\item Scalars: These are scalar variables we lift into arrays for the purposes of vectorization. 
For those, all writes are canonical writes and all reads are canonical reads. We may apply both raise dimension 
and drop dimension on these.

\item Read-only input arrays: Read-only inputs. There are NO writes, while we may have non-canonical reads, $f(i,j,k)$. 
Phase 1 of Basic vectorization will add raise dimension operation at the beginning of the function and raise dimension 
may reshape arrays. If there are multiple "views" of the input array, there could be multiple raise dimension statements to create
each one of these views. The invariant is that at reads in loops, the reads of "views" of the original input array will be canonical.
Only raise dimension applies.

 \item Read-write output arrays: Writes are canonical (by restriction) but reads can be non-canonical. Conjecture:
 do nothing. Dependence analysis takes care of limiting vectorization so non-canonical access will work. 
Still work in progress. We may apply both raise and drop dimension.

\end{itemize}

\ana{End Work-in-progress notes.}

>>>>

In the code below, all initializations (e.g., \texttt{min\_sum!3 = i}), operations, and PHI nodes are \emph{implicitly vectorized}. 
$\mathit{raise\_dim}$ and $\mathit{drop\_dim}$ statements have slightly different interpretation. %\ana{This is vague, may need elaboration.}

The example illustrates the two different versions of $\mathit{raise\_dim}$. \texttt{C!0' = raise\_dim(C!0, j, (i:N!0,j:D!0))} reshapes
the read-only input array, while \texttt{sum!3' = drop\_dim(sum!3)} removes the $j$ dimension of \texttt{sum!3}.
%\ana{More here! One just adds a least-significant dimension. The other one may reshape an input array.}

@@

%\ana{Begin Work-in-progress notes on implementation. Just some thoughts...} 
\begin{comment}
For now, I suggest we go with a "naive" implementation and try to do only minimal optimizations. 
All arrays are stored in the program as one-dimensional arrays. Arrays lifted from scalars have dimensionality of the loop enclosure in 
the original code, e.g., \texttt{sum!3} is two dimensional \texttt{[N!0,D!0]} (but represented linearly in row-major order; all these "copies" are 
arrays of references to shares). Naturally, all writes into these arrays are canonical writes, i.e., $A[i,j] = ...$ and no things like $A[i+1,j-1] = ...$.

@@

\begin{verbatim}
// project the (j-1)-st column vector:
A = sum!4[I,j-1]
// project j-th column from p!3: 
B = p!3[I,j] 
// we get a N!0-size vector of references to NEW shares:
C = ADD_SIMD(A,B) 
// Writes j-th column of sum!4 with the new references:
sum!4[I,j] = C 
// may eventually optimize since C is A
\end{verbatim}
\end{comment}

%\ana{End Work-in-progress notes.}
